Floquet-Drude Conductivity in Dressed Quantum Hall Systems

### 2021-07-23 paper/v1.0/sections/2_schrodinger_problem.tex
Add formatting and corrections

Using Landau gauge for the stationary magnetic field, we can represent it using a vector potential as $\vb{A}_{s} = (-By,0,0)^{\text{T}}$ and choosing Coulomb gauge, the vector potential of the dynamic dressing radiation can be presented as $\vb{A}_{d}(t) = (0,[E/\omega ]\cos(\omega t),0)^{\text{T}}$. These vector potentials are coupled to the momentum of 2DEG as kinetic momentum \cite{mahan00,bruus04} and this leads to the time-dependent Hamiltonian
\begin{equation} \label{eq_1}
  \hat{H}_e(t) = \frac{1}{2m_e}\Big[\hat{\vb{p}} - e\big(\vb{A}_{s}+\vb{A}_{d}(t)\big)\Big]^2,
\end{equation}
where $m_e$ is the effective electron mass and $e$ is the magnitude of the electron charge. $\hat{\vb{p}} = (\hat{p}_x,\hat{p}_y,0)^{\text{T}}$ represents the canonical momentum operator for 2DEG with electron momentum $p_{x,y}$.
The exact solutions for the time-dependent Schrödinger equation $i\hbar \dv{t}\psi = \hat{H}_e(t) \psi$ was already given by Refs. \cite{husimi53,ditt98,dini16} and we can present them as a set of wave functions defined by two quantum numbers $(n,m)$
\begin{equation} \label{eq_2}
  \begin{aligned}
    \psi_{n,m}&(x,y,t)  \\
    & = \frac{1}{\sqrt{L_x}}
    \chi_n\left[y - y_0 - \zeta(t)\right]\\
    & \times
    \text{exp}\bigg(
    \frac{i}{\hbar}\bigg[- \varepsilon_nt
    + p_x x + \frac{eE(y - y_0)}{\omega}\cos(\omega t)\\
    &+
    m_e\dot{\zeta}(t)\big[y - y_0 -\zeta(t)\big] +
    \int_0^{t}dt'L(\zeta,\dot{\zeta},t')\bigg]\bigg),
  \end{aligned}
\end{equation}
where $n \in \mathbb{Z}^{+}_0$ and $m \in \mathbb{Z}$ ; see Appendix A. Here $L_{x,y}$ are dimension of the 2DEG surface, $\hbar$ is the reduced Planck constant, and the center of the cyclotron orbit on the $y$-axis is given by $y_0 = -p_x/eB$. $\chi_n$ are well known solutions for Schrödinger equation of a stationary quantum harmonic oscillator
\begin{equation} \label{eq_3}
  \chi_n(x) \equiv
   \frac{\sqrt{\kappa}}{\sqrt{2^{n}n!}}
  e^{-\kappa^2 x^2/2}
  \mathcal{H}_n \qty(\kappa x) \quad \text{with}
  \quad
  \kappa = \sqrt{\frac{m_e \omega_0}{\hbar}},
\end{equation}
where eigenvalues are given by $\varepsilon_n = \hbar \omega_0 (n + 1/2)$ and $\omega_0 = eB/m_e$ is the cyclotron frequency. Each $n$ value defines the  energy($\varepsilon_n$) of the respective Landau level. The path shift of the driven classical oscillator $\zeta(t)$ is given by
\begin{equation} \label{eq_4}
  \zeta(t) = \frac{eE}{m_e(\omega_0^2 - \omega^2)}\sin(\omega t),
\end{equation}
while the Lagrangian of the classical oscillator $L(\zeta,\dot{\zeta},t)$ can be identified as
\begin{equation} \label{eq_5}
  L(\zeta,\dot{\zeta},t) = \frac{1}{2} m_e\dot{\zeta}^2(t) - \frac{1}{2}m_e\omega_0^2 \zeta^2(t) + eE\zeta(t) \sin(\omega t).
\end{equation}
The exponential phase shifts in Eq.~(\ref{eq_2}) represent the influence done by the stationary magnetic field and dressing field. Therefore, we can accept that magneto-transport characteristics of 2DEG can be renormalized by the nonoscillating magnetic field along with the dressing field.

>>>>

Using Landau gauge for the stationary magnetic field, we can represent it using a vector potential as $\vb{A}_{s} = (-By,0,0)^{\text{T}}$ and choosing Coulomb gauge, the vector potential of the dynamic dressing radiation can be presented as $\vb{A}_{d}(t) = (0,[E/\omega ]\cos(\omega t),0)^{\text{T}}$. These vector potentials are coupled to the momentum of 2DEG as kinetic momentum \cite{mahan00,bruus04} and this leads to the time-dependent Hamiltonian
\begin{equation} \label{eq_1}
  \hat{H}_e(t) = \frac{1}{2m_e}\Big[\hat{\vb{p}} - e\big[\vb{A}_{s}+\vb{A}_{d}(t)\big]\Big]^2,
\end{equation}
where $m_e$ is the effective electron mass and $e$ is the magnitude of the electron charge. $\hat{\vb{p}} = (\hat{p}_x,\hat{p}_y,0)^{\text{T}}$ represents the canonical momentum operator for 2DEG with electron momentum $p_{x,y}$.
The exact solutions for the time-dependent Schrödinger equation $i\hbar \dv{t}\psi = \hat{H}_e(t) \psi$ was already given by Refs. \cite{husimi53,ditt98,dini16} and we can present them as a set of wave functions defined by two quantum numbers $(n,m)$
\begin{equation} \label{eq_2}
  \begin{aligned}
    \psi_{n,m}&(x,y,t)  \\
    & = \frac{1}{\sqrt{L_x}}
    \chi_n\big(y - y_0 - \zeta(t)\big)\\
    & \times
    \text{exp}\bigg(
    \frac{i}{\hbar}\bigg[- \varepsilon_nt
    + p_x x + \frac{eE[y - y_0]}{\omega}\cos(\omega t)\\
    &+
    m_e\dot{\zeta}(t)\big[y - y_0 -\zeta(t)\big] +
    \int_0^{t}dt'L(\zeta,\dot{\zeta},t')\bigg]\bigg),
  \end{aligned}
\end{equation}
where $n \in \mathbb{Z}^{+}_0$ and $m \in \mathbb{Z}$ ; see Appendix A. Here $L_{x,y}$ are dimension of the 2DEG surface, $\hbar$ is the reduced Planck constant, and the center of the cyclotron orbit on the $y$-axis is given by $y_0 \equiv -p_x/eB$ with $p_x = 2\pi \hbar m/L_x$. $\chi_n$ are well known solutions for Schrödinger equation of a stationary quantum harmonic oscillator
\begin{equation} \label{eq_3}
  \chi_n(y) =
   \frac{\sqrt{\kappa}}{\sqrt{2^{n}n!}}
  e^{-\kappa^2 y^2/2}
  \mathcal{H}_n \qty(\kappa y) \quad \text{with}
  \quad
  \kappa = \sqrt{\frac{m_e \omega_0}{\hbar}},
\end{equation}
where eigenvalues are given by $\varepsilon_n = \hbar \omega_0 (n + 1/2)$ and $\omega_0 \equiv eB/m_e$ is the cyclotron frequency. Each $n$ value defines the occupied energy($\varepsilon_n$) of the respective Landau level. The path shift of the driven classical oscillator $\zeta(t)$ is given by
\begin{equation} \label{eq_4}
  \zeta(t) = \frac{eE}{m_e(\omega_0^2 - \omega^2)}\sin(\omega t),
\end{equation}
while the Lagrangian of the classical oscillator $L(\zeta,\dot{\zeta},t)$ can be identified as
\begin{equation} \label{eq_5}
  L(\zeta,\dot{\zeta},t) = \frac{1}{2} m_e\dot{\zeta}^2(t) - \frac{1}{2}m_e\omega_0^2 \zeta^2(t) + eE\zeta(t) \sin(\omega t).
\end{equation}
The exponential phase shifts in Eq.~(\ref{eq_2}) represent the influence done by the stationary magnetic field and dressing field. Therefore, we can accept that magneto-transport characteristics of 2DEG can be renormalized by the nonoscillating magnetic field along with the dressing field.

### 2021-07-23 paper/v1.0/sections/3_floquet_theory.tex
Add formatting and corrections

The general interpretations of physical systems are mostly derived using symmetry conditions in quantum theory. Famous Bloch analysis of electrons in quantum systems introduces a mathematical explanation of quantum systems occupying a discrete translational symmetry in configuration space. Floquet theory gives a mathematical formalism that can be used for translational symmetry in time rather than in space \cite{floquet83,grifoni98,holthaus15}. Examine the transport properties of systems exposed to strong radiation using the Floquet-Drude conductivity method introduced recently by M. Wackerl \cite{wackerl20}. In their analysis they have presented more accurate results than previously existed theoretical descriptions for the conductivity in presence of a strong dressing field. Therefore, we are hoping to apply the Floquet-Drude conductivity method to analyze our 2DEG system which is subjected to both a stationary magnetic field and a strong dressing field.

First we need to identify the \textit{quasienergies} and periodic \textit{Floquet modes} for derived wave functions in Eq.~(\ref{eq_2}). By factorizing the wave function into a linearly time dependent part and a periodic time dependent part, the quasienergies can be present as
\begin{equation} \label{eq_6}
  \varepsilon_{n} =
  \hbar \omega_0\qty(n + \frac{1}{2}) - \Delta_{\varepsilon},
\end{equation}
which is only depended on single quantum number ($n$) and Floquet modes are given by
\begin{equation} \label{eq_7}
  \begin{aligned}
    \phi_{n,m}(x,y,t) = &
    \frac{1}{\sqrt{L_x}} \chi_{n}\left[y - y_0 - \zeta(t)\right]\\
    & \times
    \text{exp}\bigg(
     \frac{i}{\hbar}\bigg[
     p_x x +
     \frac{eE(y - y_0)}{\omega}\cos(\omega t) \\
     & +
     m_e\dot{\zeta}(t)\big[y - y_0 -\zeta(t)\big]
     + \xi \bigg]\bigg),
  \end{aligned}
\end{equation}
with
\begin{equation} \label{eq_8}
  \Delta_{\varepsilon} = \frac{(eE)^2}{4m_e(\omega_0^2 - \omega^2)} ~ \text{and} ~
  \xi = \frac{(eE)^2\qty(3\omega^2 - \omega_0^2)}{8m_e\omega(\omega_0^2 - \omega^2)^2} \sin(2\omega t).
\end{equation}
It is important to notice that these Floquet modes are time-periodic ($T=2\pi/\omega$) functions. At the resonance $\omega = \omega_0$, the energy levels occupies a continuous form and the discrete quasienergies are no longer valid \cite{popov70}. Therefore, in this work we choose the dressing field frequency as $\omega \neq \omega_0$.

Then performing Fourier transform over the confined two-dimentional space $A=L_xL_y$, we obtain the momentum space($k_x,k_y$) representation of Floquet modes
\begin{equation} \label{eq_9}
  \begin{aligned}
    \phi_{n,m}(k_x,k_y,t)  = &
    {\sqrt{L_x}}
    \tilde{\chi}_{n}\qty(k_y - b\cos(\omega t)) \\
    & \times
    \text{exp}\left(
      i\xi
      -ik_y  \qty[d\sin(\omega t) + y_0]
    \right),
  \end{aligned}
\end{equation}
where
\begin{equation} \label{eq_10}
  \tilde{\chi}_{n}\qty(k) =
  \frac{i^n}{\sqrt{2^{n} n! \sqrt{\pi}}}
  \qty(\frac{1}{\kappa})^{1/2}
  e^{-\frac{k^2}{2 \kappa^2}}
  \mathcal{H}_{n} \qty(\frac{k}{\kappa})
\end{equation}
and
\begin{equation} \label{eq_11}
  b \equiv
  \frac{eE\omega_0^2}{\hbar\omega(\omega_0^2 - \omega^2)} \quad
  d \equiv
 \frac{eE}{m_e(\omega_0^2 - \omega^2)}.
\end{equation}
For details of the formalism the authors refer to Appendix B. Now using Floquet theory, the wave functions derived in Eq.~(\ref{eq_2}) can be written in momentum space as Floquet states
\begin{equation} \label{eq_12}
  \psi_{n,m}(k_x,k_y,t) =
  \exp(-\frac{i}{\hbar}\varepsilon_{n}t)   \phi_{n,m} (k_x,k_y,t).
\end{equation}

>>>>

The general interpretations of physical systems are mostly derived using symmetry conditions in quantum theory. Famous Bloch analysis of electrons in quantum systems introduces a mathematical explanation of quantum systems occupying a discrete translational symmetry in configuration space. Floquet theory gives a mathematical formalism that can be used for translational symmetry in time rather than in space \cite{floquet83,grifoni98,holthaus15}. Examine the transport properties of quantum systems exposed to strong radiation using the Floquet-Drude conductivity method introduced recently by M. Wackerl \textit{et al.} \cite{wackerl20}. In their analysis they have presented more accurate results than previously existed theoretical descriptions for the conductivity of nanoscale systems in presence of a dressing field. Therefore, we are hoping to apply the Floquet-Drude conductivity method to analyze our 2DEG system which is subjected to both a stationary magnetic field and a dressing field.

First we require to recognize the \textit{quasienergies} and time periodic \textit{Floquet modes} \cite{grifoni98} for the previously derived wave functions in Eq.~(\ref{eq_2}). By factorizing the wave function into a linearly time dependent part and a periodic time dependent part, the quasienergies can be present as
\begin{equation} \label{eq_6}
  \varepsilon_{n} =
  \hbar \omega_0\qty(n + \frac{1}{2}) - \Delta_{\varepsilon},
\end{equation}
which is only depended on a single quantum number ($n$) and Floquet modes are given by
\begin{equation} \label{eq_7}
  \begin{aligned}
    \phi_{n,m}(x,y,t) = &
    \frac{1}{\sqrt{L_x}} \chi_{n}\big(y - y_0 - \zeta(t)\big)\\
    & \times
    \text{exp}\bigg(
     \frac{i}{\hbar}\bigg[
     p_x x +
     \frac{eE[y - y_0]}{\omega}\cos(\omega t) \\
     & +
     m_e\dot{\zeta}(t)\big[y - y_0 -\zeta(t)\big]
     + \xi \bigg]\bigg),
  \end{aligned}
\end{equation}
with
\begin{equation} \label{eq_8}
  \Delta_{\varepsilon} = \frac{(eE)^2}{4m_e(\omega_0^2 - \omega^2)} ~ \text{and} ~
  \xi = \frac{(eE)^2\qty(3\omega^2 - \omega_0^2)}{8m_e\omega(\omega_0^2 - \omega^2)^2} \sin(2\omega t).
\end{equation}
It is important to notice that these Floquet modes are time-periodic ($T=2\pi/\omega$) functions. At the resonance $\omega = \omega_0$, the energy levels occupies a continuous form and the discrete quasienergies are no longer valid \cite{popov70}. Therefore, in this work we choose the dressing field frequency with the condition $\omega \neq \omega_0$.

Then performing Fourier transform over the confined two-dimentional space, we obtain the momentum space($k_x,k_y$) representation of Floquet modes
\begin{equation} \label{eq_9}
  \begin{aligned}
    \phi_{n,m}\big(k_x,k_y,t\big)  = &
    {\sqrt{L_x}}
    \tilde{\chi}_{n}\qty(k_y - b\cos(\omega t)) \\
    & \times
    \text{exp}\left(
      i\xi
      -ik_y  \qty[d\sin(\omega t) + y_0]
    \right),
  \end{aligned}
\end{equation}
where
\begin{equation} \label{eq_10}
  \tilde{\chi}_{n}\qty(k) =
  \frac{i^n}{\sqrt{2^{n} n! \sqrt{\pi}}}
  \qty(\frac{1}{\kappa})^{1/2}
  e^{-\frac{k^2}{2 \kappa^2}}
  \mathcal{H}_{n} \qty(\frac{k}{\kappa}).
\end{equation}
Here we used new parameters
\begin{equation} \label{eq_11}
  b \equiv
  \frac{eE\omega_0^2}{\hbar\omega(\omega_0^2 - \omega^2)} \quad \text{and} \quad
  d \equiv
 \frac{eE}{m_e(\omega_0^2 - \omega^2)}.
\end{equation}
For details of the full derivation please refer to Appendix B. Now using Floquet theory, the wave functions derived in Eq.~(\ref{eq_2}) can be written in momentum space as Floquet states
\begin{equation} \label{eq_12}
  \psi_{n,m}(k_x,k_y,t) =
  \exp(-\frac{i}{\hbar}\varepsilon_{n}t)   \phi_{n,m} (k_x,k_y,t).
\end{equation}

### 2021-07-23 paper/v1.0/sections/4_inverse_scattering_time.tex
Add formatting and corrections

In Ref. \cite{wackerl20} Floquet Fermi golden rule has been introduced as a method to analyze transport properties in dressed quantum systems. However, this theory has not been applied for a dressed quantum Hall system and to identify magneto-transport properties in our system we use Floquet Fermi golden rule.
With the help of $t-t'$ formalism \cite{wackerl20,grifoni98,sambe75,peskin93,althorpe97} and using Floquet states derived in Eq.~(\ref{eq_12}) we can derive an  expression for the inverse scattering time matrix ($(l,l')$th element) for the $N$th Landau level, per a given energy $\varepsilon$ and momentum $k_x$ value for our considered quantum Hall system as
\begin{equation} \label{eq_13}
  \begin{aligned}
    \bigg(&\frac{1}{\tau(\varepsilon,k_x)}\bigg)^{ll'}_{N} \\
    & =
    \frac { \varrho^2}{eB}
    \delta(\varepsilon - \varepsilon_{N}) \\
    & \times
    \int_{-\infty}^{\infty} d k_1
    J_l\qty(\frac{b\hbar}{eB}[{k}_x - k_1])
    J_{l'}\qty(\frac{b\hbar}{eB}[{k}_x - k_1]) \\
    & \times
    \qty|
    \int_{-\infty}^{\infty} dk_2 \;
    {\chi}_{N}\qty(\frac{\hbar}{eB}k_2)
    {\chi}_{N}\qty(\frac{\hbar}{eB} \qty[k_1 - {k}_x - k_2])|^2,
  \end{aligned}
\end{equation}
where $\varrho \equiv \eta_{imp} L_x [ { V_{imp}}/{eB}]^{1/2}$,
$J_l(\cdot)$ are Bessel functions of the first kind with $l$th integer order and $\varepsilon_N$ is the energy of $N$th Landau level; see Appendix C. In this study, we assume that the perturbation potential is generated by a group of randomly distributed impurities, since random impurities in a disordered metal is a better approximation for experimental results. Thus, the total scattering potential in 2DEG can be presented as the sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$. Here $\eta_{imp}$ is the number of impurities in a unit area and $V_{imp} = \expval{|V_{{k'}_x,k_x}|^2}$ with $V_{{k'}_x,k_x} = \mel**{k'_x}{\upsilon(x) }{k_x}$ where $\braket{x}{k_x} = e^{-ik_x x}/\sqrt{L_x}$.

Next we are going to analyze the contribution of the inverse scattering time matrix elements to the transport properties in 2DEG.
Since the disorder in the system can not be alter the eigenenergy values of the undressed system \cite{wackerl20}, we can neglect the all off-diagonal elements of the self-energy, and then we can consider only the central diagonal element (${l=l'=0}$) of the inverse scattering time matrix which has the largest contribution to the transport characteristics.
% \begin{equation} \label{eq_14}
%   \begin{aligned}
%     \bigg(&\frac{1}{\tau(\varepsilon,k_x)}\bigg)^{00}_{N} \\
%     & =
%     \frac { \varrho^2}{eB}
%     \delta(\varepsilon - \varepsilon_{N}) \\
%     & \times
%     \int_{-\infty}^{\infty} d k_1 \;
%     J_0^2\qty(\frac{b\hbar}{eB}[{k}_x -  k_1])
%     \\
%     & \times
%     \qty|
%     \int_{-\infty}^{\infty} d k_2 \;
%     {\chi}_{N}\qty(\frac{\hbar}{eB}k_2)
%     {\chi}_{N}\qty(\frac{\hbar}{eB} \qty[k_1 - {k}_x - k_2])|^2.
%   \end{aligned}
% \end{equation}
Introduce a new parameter as scattering-induced broadening of the $N$-th Landau level as \cite{dini16,endo09}
\begin{equation} \label{eq_14}
 \Gamma^{00}_{N}(\varepsilon,k_x) \equiv \hbar \qty(\frac{1}{\tau(\varepsilon,k_x)})^{00}_{N},
\end{equation}
and this leads to
\begin{equation} \label{eq_15}
 \begin{aligned}
   \Gamma^{00}_{N}& (\varepsilon,k_x) \\
   & =
   \frac { \varrho^2}{eB}
   \delta(\varepsilon - \varepsilon_{N}) \\
   & \times
   \int_{-\infty}^{\infty} d {k'}_x \;
   J_0^2\qty(\frac{b\hbar}{eB}[{k}_x - {k'}_x])
   \\
   & \times
   \qty|
   \int_{-\infty}^{\infty} dk_2 \;
   {\chi}_{N}\qty(\frac{\hbar}{eB}k_2)
   {\chi}_{N}\qty(\frac{\hbar}{eB} \qty[{k'}_x - {k}_x - k_2])|^2.
 \end{aligned}
\end{equation}

@@

\begin{figure}[t]
\includegraphics[scale=0.68]{figures/fig_4}
\caption{\label{fig_4} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against dressing field intensity $I$, in a GaAs-based quantum well under a nonoscillating magnetic field with $B = 1.2~\text{T}$, dressing field with frequency of $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$. In this calculation we have assumed that the natural broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$.}
\end{figure}

In addition, for a scenario of scattering take place inside the same Landau level, we are able to present the delta distribution of the energy using the same physical interpretation \cite{dini16} as follows
\begin{equation} \label{eq_16}
 \delta(\varepsilon - \varepsilon_{N}) \approx
 \frac{1}{\pi \Gamma^{00}_{N}(\varepsilon,k_x)},
\end{equation}
and we write the central element of inverse scattering time matrix in more compact form
\begin{equation} \label{eq_17}
  \begin{aligned}
    \Gamma^{00}_{N}(\varepsilon,& k_x) =
    \varrho
    \bigg[
    \int_{-\infty}^{\infty} d {k}_1 \;
    J_0^2\qty(\lambda_1[{k}_x - {k}_1]) \\
    & \times
    \qty|
    \int_{-\infty}^{\infty} d{k}_2 \;
    \tilde{\chi}_{N}\qty(\lambda_2 k_2)
    \tilde{\chi}_{N}\qty(\lambda_2 \qty[{k}_1 - {k}_2 - {k}_x])|^2
    \bigg]^{-\frac{1}{2}},
  \end{aligned}
\end{equation}
where $ \lambda_1 \equiv \hbar b/eB$ and  $\lambda_2 \equiv \hbar \kappa/eB$.
To analyze the contribution of dressing field on the scattering-induced broadening, normalized $N$-th Landau level scattering-induced broadening can be defined as
\begin{equation} \label{eq_18}
    \Lambda_N(k_x) \equiv
    \frac{\Gamma^{00}_{N}(\varepsilon,k_x)}{\Gamma^{00}_{N=0}(\varepsilon,k_x)\big|_{E=0}},
\end{equation}
and this leads to
\begin{widetext}
\begin{equation} \label{eq_19}
    \Lambda_N (k_x) =
    \qty[
    \frac
    {\int_{-\infty}^{\infty} d {k}_1 \;
    J_0^2\qty(\lambda_1[{k}_x - {k}_1])
    \qty|
    \int_{-\infty}^{\infty} d{k}_2 \;
    \tilde{\chi}_{N}\qty(\lambda_2 k_2)
    \tilde{\chi}_{N}\qty(\lambda_2 \qty[{k}_1 - {k}_2 - {k}_x])|^2}
    {\int_{-\infty}^{\infty} d {k}_1 \;
    \qty|
    \int_{-\infty}^{\infty} d{k}_2 \;
    \tilde{\chi}_{0}\qty(\lambda_2 k_2)
    \tilde{\chi}_{0}\qty(\lambda_2 \qty[{k}_1 - {k}_2 - {k}_x])|^2}
    ]^{1/2}.
\end{equation}
\end{widetext}

Normalized energy band broadening against ${k_x}$ for different Landau levels ($N = 0,1,2,3,4$) has been calculated for GaAs-based quantum well and results are given in Fig.~(\ref{fig_3}) and Fig.~(\ref{fig_4}). To make comparison we have selected the experiment parameters to match with analysis done in Ref.~\cite{endo09}.
In their study, they have assumed that effective mass of the electron in GaAs-based quantum well system is $m_e = 0.07m$ where $m$ is mass of the electron \cite{endo09,winkler03,wackerl20} and the broadening of the natural(without a dressing field) $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$. Therefore, in our calculations, we assumed that the natural least Landau level broadening also has this value: $\Gamma^{00}_{N=0}|_{E=0} = 0.24 \;\text{meV}$.
Here we can identify that we can change each Landau level normalized energy broadening value using applied electromagnetic field. When the applied field's intensity increase the energy broadening gets reduced which make changes in conductivity of 2DEG.

>>>>

In Ref. \cite{wackerl20} Floquet Fermi golden rule has been introduced as a method to analyze transport properties in dressed disordered quantum systems. However, this theory has not been applied for a dressed quantum Hall system and to identify magneto-transport properties in our system we use Floquet Fermi golden rule.
With the help of $t-t'$ formalism \cite{wackerl20,grifoni98,sambe75,peskin93,althorpe97} and using Floquet states derived in Eq.~(\ref{eq_12}) we can derive an  expression for the inverse scattering time matrix ($(l,l')$th element) for the $N$-th Landau level, per a given energy $\varepsilon$ and momentum $k_x$ value for our considered quantum Hall system as
\begin{equation} \label{eq_13}
  \begin{aligned}
    \bigg(&\frac{1}{\tau(\varepsilon,k_x)}\bigg)^{ll'}_{N} \\
    & =
    \frac { \varrho^2}{eB}
    \delta(\varepsilon - \varepsilon_{N}) \\
    & \times
    \int_{-\infty}^{\infty} d k_1 \Bigg[
    J_l\qty(\frac{b\hbar}{eB}[{k}_x - k_1])
    J_{l'}\qty(\frac{b\hbar}{eB}[{k}_x - k_1]) \\
    & \times
    \qty|
    \int_{-\infty}^{\infty} dk_2 \;
    {\chi}_{N}\qty(\frac{\hbar}{eB}k_2)
    {\chi}_{N}\qty(\frac{\hbar}{eB} \qty[k_1 - {k}_x - k_2])|^2\Bigg],
  \end{aligned}
\end{equation}
where $\varrho \equiv \eta_{imp} L_x [ { V_{imp}}/{eB}]^{1/2}$,
$J_l(\cdot)$ are Bessel functions of the first kind with $l$-th integer order and $\varepsilon_N$ is the energy of $N$-th Landau level; see Appendix C. In this derivation, we assumed that the perturbation potential is generated by a group of randomly distributed impurities, since random impurities in a disordered metal is a better approximation for experimental results. Thus, the total scattering potential in 2DEG has been presented as the sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$. Here $\eta_{imp}$ is the number of impurities in a unit area and $V_{imp} \equiv \expval{|V_{{k'}_x,k_x}|^2}$ with $V_{{k'}_x,k_x} = \mel**{k'_x}{\upsilon(x) }{k_x}$ where $\braket{x}{k_x} = e^{-ik_x x}/\sqrt{L_x}$.

Next we are going to analyze the contribution of the inverse scattering time matrix elements to the transport properties in 2DEG.
Since the disorder in the system can not be alter the eigenenergy values of the undressed system \cite{wackerl20}, we can neglect the all off-diagonal elements of the self-energy, and then we can consider only the central diagonal element (${l=l'=0}$) of the inverse scattering time matrix which has the largest contribution to the transport characteristics.
% \begin{equation} \label{eq_14}
%   \begin{aligned}
%     \bigg(&\frac{1}{\tau(\varepsilon,k_x)}\bigg)^{00}_{N} \\
%     & =
%     \frac { \varrho^2}{eB}
%     \delta(\varepsilon - \varepsilon_{N}) \\
%     & \times
%     \int_{-\infty}^{\infty} d k_1 \;
%     J_0^2\qty(\frac{b\hbar}{eB}[{k}_x -  k_1])
%     \\
%     & \times
%     \qty|
%     \int_{-\infty}^{\infty} d k_2 \;
%     {\chi}_{N}\qty(\frac{\hbar}{eB}k_2)
%     {\chi}_{N}\qty(\frac{\hbar}{eB} \qty[k_1 - {k}_x - k_2])|^2.
%   \end{aligned}
% \end{equation}
Introduce a new parameter as scattering-induced broadening of the $N$-th Landau level as \cite{dini16,endo09}
\begin{equation} \label{eq_14}
 \Gamma^{00}_{N}(\varepsilon,k_x) = \hbar \qty(\frac{1}{\tau(\varepsilon,k_x)})^{00}_{N},
\end{equation}
and this leads to
\begin{equation} \label{eq_15}
 \begin{aligned}
   \Gamma^{00}_{N}& (\varepsilon,k_x) \\
   & =
   \frac { \varrho^2}{eB}
   \delta(\varepsilon - \varepsilon_{N}) \\
   & \times
   \int_{-\infty}^{\infty} d k_1 \Bigg[
   J_0^2\qty(\frac{b\hbar}{eB}[{k}_x - k_1])
   \\
   & \times
   \qty|
   \int_{-\infty}^{\infty} dk_2 \;
   {\chi}_{N}\qty(\frac{\hbar}{eB}k_2)
   {\chi}_{N}\qty(\frac{\hbar}{eB} \qty[k_1 - {k}_x - k_2])|^2\Bigg].
 \end{aligned}
\end{equation}

@@

\begin{figure}[b]
\includegraphics[scale=0.68]{figures/fig_4}
\caption{\label{fig_4} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against dressing field intensity $I$, in a GaAs-based quantum well under a nonoscillating magnetic field with $B = 1.2~\text{T}$, dressing field with frequency of $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$. In this calculation we have assumed that the natural broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$.}
\end{figure}

In addition, for a scenario of scattering take place inside the same Landau level, we are able to present the delta distribution of the energy using the following interpretation \cite{dini16}
\begin{equation} \label{eq_16}
 \delta(\varepsilon - \varepsilon_{N}) \approx
 \frac{1}{\pi \Gamma^{00}_{N}(\varepsilon,k_x)},
\end{equation}
and we write the central element of inverse scattering time matrix in more compact form
\begin{equation} \label{eq_17}
  \begin{aligned}
    \Gamma^{00}_{N}(\varepsilon,& k_x) =
    \varrho
    \bigg[
    \int_{-\infty}^{\infty} d {k}_1 \;
    J_0^2\qty(\lambda_1[{k}_x - {k}_1]) \\
    & \times
    \qty|
    \int_{-\infty}^{\infty} d{k}_2 \;
    \tilde{\chi}_{N}\qty(\lambda_2 k_2)
    \tilde{\chi}_{N}\qty(\lambda_2 \qty[{k}_1 - {k}_2 - {k}_x])|^2
    \bigg]^{-\frac{1}{2}},
  \end{aligned}
\end{equation}
where $ \lambda_1 \equiv \hbar b/eB$ and  $\lambda_2 \equiv \hbar \kappa/eB$.
To analyze the contribution of dressing field on the scattering-induced broadening, normalized $N$-th Landau level scattering-induced broadening can be defined as
\begin{equation} \label{eq_18}
    \Lambda_N(k_x) \equiv
    \frac{\Gamma^{00}_{N}(\varepsilon,k_x)}{\Gamma^{00}_{N=0}(\varepsilon,k_x)\big|_{E=0}},
\end{equation}
and this leads to
\begin{widetext}
\begin{equation} \label{eq_19}
    \Lambda_N (k_x) =
    \qty[
    \frac
    {\int_{-\infty}^{\infty} d {k}_1 \;
    J_0^2\qty(\lambda_1[{k}_x - {k}_1])
    \qty|
    \int_{-\infty}^{\infty} d{k}_2 \;
    \tilde{\chi}_{N}\qty(\lambda_2 k_2)
    \tilde{\chi}_{N}\qty(\lambda_2 \qty[{k}_1 - {k}_2 - {k}_x])|^2}
    {\int_{-\infty}^{\infty} d {k}_1 \;
    \qty|
    \int_{-\infty}^{\infty} d{k}_2 \;
    \tilde{\chi}_{0}\qty(\lambda_2 k_2)
    \tilde{\chi}_{0}\qty(\lambda_2 \qty[{k}_1 - {k}_2 - {k}_x])|^2}
    ]^{1/2}.
\end{equation}
\end{widetext}

Normalized energy band broadening against ${k_x}$ for different Landau levels ($N = 0,1,2,3,4$) has been calculated for GaAs-based quantum well and results are given in Fig.~(\ref{fig_3}) and Fig.~(\ref{fig_4}). To make comparison we have selected the experiment parameters to match with analysis done in Ref.~\cite{endo09}.
In their study, they have assumed that effective mass of the electron in GaAs-based quantum well system is $m_e \approx 0.07\tilde{m}_e$ where $\tilde{m}_e$ is mass of the electron \cite{endo09,winkler03,wackerl20} and the broadening of the natural(without a dressing field) $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$. Therefore, in our calculations, we assumed that the natural least Landau level broadening also has this value: $\Gamma^{00}_{N=0}|_{E=0} = 0.24 \;\text{meV}$.
Here we can identify that the each Landau level normalized energy broadening value is independent of the x-directional momentum $k_x$ value and we are able to change it using applied electromagnetic field. When the applied field's intensity increase the energy broadening gets reduced which make changes in transport properties and in the next section, we are going to derive a analytical expression for the conductivity in dressed quantum Hall systems.
